---
title: ""
output: github_document
---
# model depot <img src = "vignette/img/mrgsolve_hex.png" align="right" width="120px"></img>

mrgsolve has a function called `modlib()` that returns path 
to a library of precoded models that can be accessed like this

```{r, eval=FALSE}
mod <- mread("pk1", modlib())
```

or more concisely

```{r, eval=FALSE}
mod <- modlib("pk1")
```

__depot__ works just like `modlib()`, but the models come in a 
separate package housed here. For example

```{r, eval = FALSE}
mod <- depot("gcsf")
```

Please see the vignettes for the models listed below.  More models to come. 

# INSTALLATION
```{r, eval=FALSE}
remotes::install_github("mrgsolve/depot", subdir = "pkg")
```

## MODELS

## azithro 

- Type: Population PK
- Links: [model](pkg/inst/models/azithro.cpp) [vignette](vignette/azithro.md)

__Reference__
Zhao Q, Tensfeldt TG, Chandra R, Mould DR. _Population 
pharmacokinetics of azithromycin and chloroquine in healthy adults and paediatric
malaria subjects following oral administration of fixed-dose azithromycin and 
chloroquine combination tablets_. Malar J. 2014 Jan 29;13:36. 
doi:10.1186/1475-2875-13-36. PubMed PMID: 24472224; PubMed Central 
PMCID: PMC3909452.


## cipro 
- Type: PBPK
- Links: [model](pkg/inst/models/cipro.cpp) [vignette](vignette/cipro.md)

__Reference__
Sadiq MW, Nielsen EI, Khachman D, Conil JM, Georges B, Houin G, Laffont CM,
Karlsson MO, Friberg LE. A whole-body physiologically based pharmacokinetic
(WB-PBPK) model of ciprofloxacin: a step towards predicting bacterial killing at 
sites of infection. J Pharmacokinet Pharmacodyn. 2017 Apr;44(2):69-79. doi:
10.1007/s10928-016-9486-9. Epub 2016 Aug 30. PubMed PMID: 27578330; PubMed
Central PMCID: PMC5376394.

## gcsf

- Type: TMDD
- Links: [model](pkg/inst/models/gcsf.cpp) [vignette](vignette/gcsf.md)

__Reference__
Krzyzanski W, Wiczling P, Lowe P, Pigeolet E, Fink M, Berghout A, Balser S.
Population modeling of filgrastim PK-PD in healthy adults following intravenous
and subcutaneous administrations. J Clin Pharmacol. 
2010 Sep;50(9 Suppl):101S-112S. doi: 10.1177/0091270010376966. 
PubMed PMID: 20881223.

## sunit

- Type: Population PK
- Links:[model](pkg/inst/models/sunit.cpp) [vignette](vignette/sunit.md)

__Reference__
Houk BE, Bello CL, Kang D, Amantea M. A population pharmacokinetic
meta-analysis of sunitinib malate (SU11248) and its primary metabolite
(SU12662) in healthy volunteers and oncology patients. Clin Cancer Res. 
2009 Apr 1;15(7):2497-506. doi: 10.1158/1078-0432.CCR-08-1893. Epub 2009 
Mar 3. PubMed PMID: 19258444.

## secukinumab

- Type: PK/PD
- Links: [model](pkg/inst/models/secukinumab.cpp) [vignette](vignette/secukinumab.md)

__Reference__

FDA Clin Pharm Review 125504Orig1s000ClinPharmR.pdf

  - Clinical Pharmacology Reviewer: Jie Wang, Ph.D.
  - Pharmcometrics Reviewer: Jee Eun Lee, Ph.D.
  - Pharmacometrics Team Leader: Jeffry Florian, Ph.D.
  - Clinical Pharmacology Team Leader: Yow-Ming Wang, Ph.D.
  
https://www.accessdata.fda.gov/drugsatfda_docs/nda/2015/125504Orig1s000ClinPharmR.pdf

## rifampicin

- Type: PBPK
- Links: [model](pkg/inst/models/rifampicin.cpp) [vignette](vignette/rifampicin.md)

__Reference__
Asaumi R, Toshimoto K, Tobe Y, Hashizume K, Nunoya KI, Imawaka H, Lee W,
Sugiyama Y. Comprehensive PBPK Model of Rifampicin for Quantitative Prediction of
Complex Drug-Drug Interactions: CYP3A/2C9 Induction and OATP Inhibition Effects. 
CPT Pharmacometrics Syst Pharmacol. 2018 Mar;7(3):186-196. doi:
10.1002/psp4.12275. Epub 2018 Feb 5. PubMed PMID: 29368402; PubMed Central PMCID:
PMC5869557.

## moxi

- Type: Population PK
- Links: [model](pkg/inst/models/moxi.cpp) [vignette](vignette/moxi.md)


__Reference__
Wicha SG, Haak T, Zink K, Kees F, Kloft C, Kees MG. Population
pharmacokinetics and target attainment analysis of moxifloxacin in patients with 
diabetic foot infections. J Clin Pharmacol. 2015 Jun;55(6):639-46.
doi:10.1002/jcph.464. Epub 2015 Feb 13. PubMed PMID: 25600294.


## opg

- Type: PK/PD
- Links: [model](pkg/inst/models/opg.cpp) [vignette](vignette/opg.md)

__Reference__

Zierhut ML, Gastonguay MR, Martin SW, Vicini P, Bekker PJ, Holloway D, Leese
PT, Peterson MC. Population PK-PD model for Fc-osteoprotegerin in healthy
postmenopausal women. J Pharmacokinet Pharmacodyn. 2008 Aug;35(4):379-99. 
doi: 10.1007/s10928-008-9093-5. Epub 2008 Jul 17. PubMed PMID: 18633695.

