---
title: "Model: tmdd"
output: 
  github_document: 
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, comment = '.')
```


# Reference

__Note__: this is the general, fully-parameterized TMDD model.

```{}
Peletier LA, Gabrielsson J. Dynamics of target-mediated drug
disposition: characteristic profiles and parameter identification. 
J Pharmacokinet Pharmacodyn. 2012 Oct;39(5):429-51. 
doi: 10.1007/s10928-012-9260-6. Epub 2012 Aug 1. PMID: 22851162; 
PMCID: PMC3446204.
```

# Example

This simulation replicates Figure 3 in the paper.


```{r}
library(depot)
library(dplyr)
library(mrgsim.sa)
```

```{r}
mod <- depot("tmdd", end = 600, delta = 0.1) 
```


Doses

- 1.5 mg/kg
- 5.0 mg/kg
- 15 mg/kg
- 45 mg/kg

```{r}
e <- expand.ev(amt = c(1.5, 5, 15, 45))
```

Note that these are mg/kg doses. Model parameters are also weight-normalized. 


```{r}
mod %>% mrgsim_e(e) %>% plot(L ~time, logy = TRUE)
```

# Sensitivity analysis

- Run on just the 5 mg/kg dose
- each parameter is varied between $\pm 2\sigma$ of log-normal
distribution with 100% coefficient of variation

```{r}
out <- mod %>%  
  parseq_cv(keRL, koff, kon, kout, kin, CL,   .cv = 100) %>%
  ev(amt = 5) %>% 
  update(outvars = "L") %>%
  sens_each(recsort = 3) 
```


```{r}
#| fig.width: 8
sens_plot(
  out, 
  "L", 
  logy = TRUE, 
  plot_ref = FALSE,
  xlab = "Time (h)", 
  ylab = "Concentration (mg/L)"
) 

```

Check the actual values

```{r}
out %>% 
  filter(time==0) %>% 
  group_by(p_name) %>% 
  summarise(
    lo = min(p_value), 
    mid = median(p_value), 
    hi = max(p_value)
  ) %>% knitr::kable()
```


# Code

```{c, eval = FALSE, code = mod@code}

```
